---
title: "Coverage and Prioritisation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Coverage and Prioritisation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, echo = TRUE, results = "hide", warning = FALSE, message = FALSE}
library(nimue)
library(ggplot2)
library(dplyr)
```

The nimue model allows us to specify age-dependent and prioritised coverage targets. These are defined by using the 
`vaccine_coverage_mat` argument. This is a coverage prioritisation matrix, with each column representing one of the
17 5-year age groups in the model and each row representing a step in our prioritisation. The model will vaccinate
all age groups in the current prioritisation step until all target coverages in that step have been achieved, at which 
point it will move to the next prioritisation step. The default `vaccine_coverage_mat`
is a simple matrix with a single prioritisation step (row) and all values 0.8 - in this cases we target all age-groups at
the same time and continue vaccinating until all have achieved 80% coverage.

Nimue, includes some built-in prioritisation matrices, which are a good place to start to understand how to
parameterise more complex strategies. See `?strategy_matrix` for all options

### Targeting the elderly first

``` {r, fig.width = 7, fig.height = 5, fig.align = "center",}
# Parameterise a strategy matrix
elderly <- strategy_matrix(strategy = "Elderly",
                           max_coverage = 0.8)

# Visualise
plot_matrix <- function(mat){
  age_labels <- c(paste0(seq(0, 75, 5), "-", seq(5, 80, 5)), "80+")
  colnames(mat) <- age_labels
  rownames(mat) <- 1:nrow(mat)
  pd <- as.data.frame.table(mat)
  colnames(pd) <- c("Prioritisation step", "Age group", "Coverage")
  ggplot(pd, aes(y = `Prioritisation step`, x = `Age group`, fill = Coverage)) +
    geom_tile() +
    theme_bw() +
    theme(axis.text.x=element_text(angle = -90, vjust = 0.3))
}

plot_matrix(elderly)
```

### Targeting at-risk, elderly, working-age then children

Prioritise a sub-population of those of working age, followed by the elderly and continuing in a stepwise fashion, moving from the oldest age group down

``` {r, fig.width = 7, fig.height = 5, fig.align = "center",}
# Parameterise a strategy matrix
at_risk <- strategy_matrix(strategy = "Risk Elderly Working Children step",
                           max_coverage = 0.8,
                           risk_proportion = 0.1)

# Visualise
plot_matrix(at_risk)
```
