---
title: "Supply"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Supply}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, echo = TRUE, results = "hide", warning = FALSE, message = FALSE}
library(nimue)
library(ggplot2)
library(dplyr)
```

We can model a scale-up of supply capacity for vaccines

### No initial supply constraint

To begin, we can run the model with no supply constraints - in this case we immediately have the ability to vaccinate 100,000 individuals per day:

```{r, echo = TRUE}
# Run the with no vaccine supply constraint
constant <- run(
  country = "United Kingdom",
  max_vaccine = 100000,
  vaccine_efficacy_disease = rep(0, 17),
  vaccine_efficacy_infection = rep(0.9, 17)
)
# Format the output selecting vaccines and deaths
o1 <- format(constant, compartments = NULL, summaries = c("deaths", "vaccines")) %>%
  mutate(Name = "Constant")

```

### Initial supply constraint

A more realistic scenario might see us ramp up our supply capcity over time, in this case ramping up to our target of vaccinating 100,000 people per day
over a period of 100 days:

```{r, echo = TRUE}
# Run with initial vaccine supply constraints
increasing <- run(
  country = "United Kingdom",
  max_vaccine = seq(0, 100000, length.out = 100),
  tt_vaccine = seq(0, 100, length.out = 100),
  vaccine_efficacy_disease = rep(0, 17),
  vaccine_efficacy_infection = rep(0.9, 17)
)
# Format the output selecting vaccines and deaths
o2 <- format(increasing, compartments = NULL, summaries = c("deaths", "vaccines")) %>%
  mutate(Name = "Increasing")

```

### Compare
```{r, echo = TRUE, fig.width = 7, fig.height = 3, fig.align = "center", warning = FALSE}
# Create plot data.frame
pd <- bind_rows(o1, o2)
# Plot outputs
ggplot(pd, aes(x = t, y = value, col = Name)) +
  geom_line(size = 1) +
  facet_wrap(~ compartment, scales = "free_y") +
  ylab("Time") +
  theme_bw()
```
